### 2022-09-25 Documents/Paper/paper.Rnw
fix paper cit

The development and implementation of this approach are of particular interest because although it has limits, it allows researchers to directly evaluate their expectations and hypotheses. The available literature, however, is rather technical. These articles' complexity makes it difficult for researchers not familiar with this approach to clearly understand all the steps involved. On the other hand, articles offering a general introduction to the Bayes factor do not provide enough details to allow readers to autonomously apply this method to their problems; instead, they usually rely on ad hoc solutions implemented in some statistical software. For example, \textcite{hoijtinkTutorialTestingHypotheses2019a} offered an excellent introduction to the Bayes factor for the evaluation of informative hypotheses using the R package \texttt{bain}. However, it is limited to the context of analysis-of-variance models, and it is not possible to extend its use to other cases.

>>>>

The development and implementation of this approach are of particular interest because although it has limits, it allows researchers to directly evaluate their expectations and hypotheses. The available literature, however, is rather technical. These articles' complexity makes it difficult for researchers not familiar with this approach to clearly understand all the steps involved. On the other hand, articles offering a general introduction to the Bayes factor do not provide enough details to allow readers to autonomously apply this method to their problems; instead, they usually rely on ad hoc solutions implemented in some statistical software. For example, \textcite{hoijtinkTutorialTestingHypotheses2019} offered an excellent introduction to the Bayes factor for the evaluation of informative hypotheses using the R package \texttt{bain}. However, it is limited to the context of analysis-of-variance models, and it is not possible to extend its use to other cases.

### 2022-09-25 README.Rmd
coorrige read me
fix paper cit

# Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

@@

Moreover, the analysis workflow is managed using `drake` (see Section below) and include other (*non-standard*) folders to organize the scripts for the analysis and for the produced outputs (i.e., paper and supplemental material).

@@

- `Analysis/` - includes the file `Analysis_Drake.R` used to run the analysis workflow using `drake`
- `Data/` - includes the data used in the analyses
- `Documents/` - includes all the scripts and utility files for the creation of the outputs. In particular,
  - `Bookdown/` - the Supplemental Material available online
  - `Paper/` - the pre-print version of the article
- `R/` - includes all the `.R` scripts with the functions used in the analyses
- `docs/` - includes `bookdown` outputs used to build the GitHub Pages site
- `renv/` - utility folder used by `renv`

@@

To guarantee the reproducibility of the results, the R-package`drake` is used to manage the analysis workflow and to enhance the readability and transparency of the analysis. To know more about `drake` consider the [official Git-hub page](https://github.com/ropensci/drake) or the [user manual](https://books.ropensci.org/drake/). Summarizing, using `drake` the user defines the plan of the analysis where each step in the analysis is defined through functions. Functions can be appropriately defined to obtain desired targets (i.e., R-output with results of interests) and they are declared in another script. Subsequently, `drake` manages the whole analysis recognizing the dependency structure of the different targets. When any change is made to the code `drake` evaluates the analysis and updates the results. Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis) allows us to avoid "*coping and paste*" in the code, it makes debugging easier, and it facilitates the reading of the code.

Moreover, the R-package `renv` is used to manage the dependencies of the R-packages used in the analysis. The `renv` package allows the creation of an isolated, portable, and reproducible environment where the analyses are run. To know more about `renv` consider the [official documentation](https://rstudio.github.io/renv/articles/renv.html). However, `renv` is limited as it can not handle different R versions.

@@

1. Download the repository on your local machine
    ```{bash, eval = FALSE}
    git clone https://github.com/ClaudioZandonella/Attachment
    ```
1. Open the R project by double-clicking the file `Attachment.Rproj` you can find in the project main directory. A new R-studio session will open.
1. Run `renv::restore()` to install the project's dependencies (have a coffee, it takes some time).
1. Now the required package will be loaded. Restart the R session (`command`/`ctrl` + `shift` + `f10`) so `devtools::load_all()` is automatically run (according to `.Rprofile`) to load all functions used in the analysis defined in the `R/` folder.

    > Note that also `source("Documents/Utils_report.R")` is automatically run to load report utility functions (functions to load analysis results and to compile the bookdown).

1. Open `Analysis/Analysis_Drake.R` and run each line (one by one) to run the analysis using drake. First, the analysis environment is set together with the analysis plan (available at `R/Plan.R`). Next, the analysis targets are computed (have a coffee, it takes a long time). Finally, the analysis results are loaded and briefly presented.

    > Note that you can access the analysis targets using the functions `drake::loadd(<name_target>)`, or load all the results with `drake_load_all()`.

    > It could happen that sometimes the session stays idle when fitting `brms` models without throwing errors. In this case, it is necessary to force restarting the R session and rerun the analysis. An error warning message will appear: `Error: drake's cache is locked`. Just follow the instructions provided by drake to force unlock of the cache  `drake::drake_cache("...")$unlock()`.

1. To compile the pre-print version of the article (possible after the analysis), open `Documents/Paper/Paper.Rnw` and compile the file using `knitr` and `pdfLaTeX` (see [project options](https://support.rstudio.com/hc/en-us/articles/200532247-Weaving-Rnw-Files-in-the-RStudio-IDE)). Note that, as usual for LaTeX files, the first run will fail. Run again to obtain the actual output. 
1. To compile the Supplemental Material, run `make_my_book()`. The resulting output is saved in the `docs/` folder.

>>>>

# Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

@@

Moreover, the analysis workflow is managed using `targets` (see Section below) and include other (*non-standard*) folders to organize the scripts for the analysis and for the produced outputs (i.e., paper and supplemental material).

@@

- `Analysis/`that includes the files
    - `Targets-workflow.R` the workflow of the analysis 
    - `Targets-analysis.R` script to run the analysis with `targets`
- `Data/` - includes the data used in the analyses
- `Documents/` - includes all the scripts and utility files for the creation of the outputs. In particular,
  - `Bookdown/` - the Supplemental Material available online
  - `Paper/` - the pre-print version of the article
- `R/` - includes all the `.R` scripts with the functions used in the analyses
  - `Targets-utils.R` functions used to load results of the analysis
- `docs/` - includes `bookdown` outputs used to build the GitHub Pages site
- `renv/` - utility folder used by `renv`

@@

To guarantee the reproducibility of the results, the R-package`targets` is used to manage the analysis workflow and to enhance the readability and transparency of the analysis. To know more about `targets` consider the [official Git-hub page](https://github.com/ropensci/targets) or the [user manual](https://books.ropensci.org/targets/). Summarizing, using `targets` the user defines the plan of the analysis where each step in the analysis is defined through functions. Functions can be appropriately defined to obtain desired targets (i.e., R-output with results of interests) and they are declared in the file `Targets-workflow.R`. Subsequently, `targets` manages the whole analysis recognizing the dependency structure of the different targets. When any change is made to the code `targets` evaluates the analysis and updates the results. Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis) allows us to avoid "*coping and paste*" in the code, makes debugging easier, and facilitates the reading of the code.

Moreover, the R-package `renv` is used to manage the dependencies of the R-packages used in the analysis. The `renv` package allows to create an isolated, portable, and reproducible environment where the analyses are run. To know more about `renv` consider the [official documentation](https://rstudio.github.io/renv/articles/renv.html). However, `renv` is limited as it can not handle different R versions.

@@

1. Download the repository on your local machine
    ```{bash, eval = FALSE}
    git clone https://github.com/ClaudioZandonella/Attachment
    ```
1. Open the R project by double-clicking the file `Attachment.Rproj` you can find in the project main directory. A new R-studio session will open.
1. Run `renv::restore()` to install the project's dependencies (have a coffee, it takes some time).
1. Now the required packages are installed. Restart the R session (`command`/`ctrl` + `shift` + `f10`) so `devtools::load_all()` is automatically run to load all functions used in the analysis defined in the `R/` folder and required packages are loaded (according to `.Rprofile`).

    > Note that also `source("Analysis/Utils_targets.R")` is automatically run to load `targets` utilities functions (functions to load analysis results). You can also use the shortcut ` Ctrl/Cmd + Shift + L` to run `devtools::load_all()`

1. Open `Analysis/Analysis_targets.R` and run each line (one by one) to run the analysis using `targets`. First, the analysis plan  is checked (available at `Analysis/Targets-workflow.R`). Next, the analysis targets are computed. Finally, the analysis results are loaded and briefly presented.

    > Note that you can access the analysis targets using the functions `targets::tar_load(<name_target>)`, or load all the results with `tar_load_all()`.

1. To compile the pre-print version of the article (possible after the analysis), open `Documents/Paper/Paper.Rnw` and compile the file using `knitr` and `pdfLaTeX` (see [project options](https://support.rstudio.com/hc/en-us/articles/200532247-Weaving-Rnw-Files-in-the-RStudio-IDE)). Note that, as usual for LaTeX files, the first run will fail. Run again to obtain the actual output.

1. To compile the Supplemental Material, run `make_my_book()`. The resulting output is saved in the `docs/` folder.
